Effects of Sudakov form factor in\\ the Golec-Biernat W\"usthoff saturation model

### 2022-09-15 Document/Effects of Sudakov form factor in the Golec-Biernat Wusthoff model.tex
plots all fine

\usepackage[table]{xcolor}
\usepackage[utf8]{inputenc}
%\usepackage{multicol}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{fancyhdr}
%\usepackage{tabularx,ragged2e,booktabs,caption}
%\usepackage{breqn}
\usepackage{graphicx}
%\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{physics}
\usepackage{hyperref}
\usepackage{ragged2e}
\usepackage{framed}
\usepackage{float}
\usepackage{rotating}
\usepackage[
%backend=bibtex,
%style=ieee
backend=bibtex,
style=phys
]{biblatex}
\addbibresource{./ref/golec.bib}
\addbibresource{./ref/gbw1998.bib}
\addbibresource{./ref/bgk2002.bib}
\addbibresource{./ref/impact.bib}
\addbibresource{./ref/cambqcd.bib}
\addbibresource{./ref/gbs2018.bib}
\addbibresource{./ref/gbs2006.bib}
\addbibresource{./ref/xiao2017.bib}
\addbibresource{./ref/minuit.bib}
\addbibresource{./ref/hera.bib}
\addbibresource{./ref/jk2006.bib}

\addbibresource{./ref/stasto2018.bib}
\addbibresource{./ref/stebel2020.bib}
\addbibresource{./ref/ellis1996.bib}
\addbibresource{./ref/bronstein.bib}
\addbibresource{./ref/mueller2016.bib}
\addbibresource{./ref/css1985.bib}
\addbibresource{./ref/prokudin2015.bib}
\addbibresource{./ref/collins2016.bib}

\newcommand{\pairdot}[2]{ \mathbf{#1}\cdot\mathbf{#2}  }
\begin{document}
\author{Tomoki Goda}
\title{ Effects of Sudakov form factor in\\ the
Golec-Biernat W\"usthoff saturation model}
\date{\today}
%\frontmatter
\maketitle
%\tableofcontents

@@

\section{GBW and BGK models }
In Ref.~\cite{gbw1998}, the following form of the dipole cross-section was proposed:
\begin{equation}
\sigma_{\mathrm{GBW}}(x ,r )=\sigma_{0} \left(1-e^{-\frac{r^2}{4} Q_0^2\left(\frac{x_0}{x}\right)^{\lambda} }\right),
\label{eq:gbw}
\end{equation}
and the modified variable 
\begin{equation}
x_m=x \left(1+\frac{4 m_f^2}{Q^2}\right),
\label{eq:modx}
\end{equation}
where $m_f$ is an effective mass of a quark $f$,
was used in place of the Bjorken scaling variable $x$. In the rest of this paper, the subscript $m$ is dropped. Along with the above modification, effective mass of the light quarks $m_l=0.14\mathrm{GeV}$ was introduced in order to study the photoproduction limit ($Q^2\rightarrow0$) of DIS.

The GBW model incorporates two main features which characterize two regions of $r$ separated by the saturation scale $Q_s(x)$, which we discuss in detail later.
%\begin{itemize} 
%\item $\sigma_{\mathrm{GBW}}(x,r)|_{r\rightarrow 0 }\sim\frac{r^2}{4}Q_0 ^2\left(\frac{x_0}{x}\right)^{\lambda} $,
%\item $\sigma_{\mathrm{GBW}} (x,r)\sim \sigma_0 $ as $r$ rises ($r\sim 1$ fm).% \cite{golec}).
%\end{itemize}
The first behaviour, 
\begin{align}
&& \sigma(x,r)&\sim r^2 & r&\ll 2/Q_s(x),
\end{align}
is related to the QCD (colour transparency), that is to say that the smaller the dipole, the less visible (colourless) it is to the target. 
The second behaviour,
\begin{align}
&& \sigma(x,r)&\sim \sigma_0 & r&\gg 2/Q_s(x),
\end{align}
is related to the saturation phenomenon. \\
%{\color{green} move the folloing part to the section Saturation Scale ...}
%{\color{gray}
%The saturation scale $Q_s(x)$, which is an energy scale, below which saturation effects are important, was defined in terms of $r=R_0(x)$ where it was related to the saturation scale as
%\begin{equation}
%R_0(x)=2/Q_s(x).
%\end{equation}
%The model was constructed such that the saturation scale satisfies the condition
%\begin{equation}
%\frac{r^2}{4} Q_0^2\left(\frac{x_0}{x}\right)^{\lambda} =1.
%\label{eq:satdef}
%\end{equation}
%Hence,
%\begin{equation}
%Q_s^2(x) =Q_0^2\left(\frac{x_0}{x}\right)^{\lambda}.
%\end{equation}
%The variables $r$ and  $Q$ are related in a way that the $z$ -integrated integrand in Eq.~(\ref{eq:factorization}) peaks around $r=2/Q$. Therefore one expects the behavoir of the dipole cross-section to be affect in the reigon about $Q^2\sim1/r^2$.
%}

%\subsection{Bartels Golec-Biernat Kowalski (DGLAP improved) Model }

%As it will be discussed later in detail (cf. Eq. \ref{eq:smallr}), in the small $r$ limit\cite{bgk2002}, 
The GBW model in the small-$r$ limit behaves as 
\begin{equation}
\sigma_{\mathrm{GBW}}\simeq\frac{r^2}{4} Q_0^2\left(\frac{x_0}{x}\right)^{\lambda}.
\end{equation}
However, the small-$r$ limit of the dipole cross-section is \cite{bgk2002}, 
\begin{equation}
\sigma_{\mathrm{dp}}(x,r)\simeq \frac{\pi^2 r^2\alpha_s(\mu^2) x g(x,\mu^2)}{3},
\end{equation}
where $g(x,\mu^2)$ is the integrated gluon distribution at the scale $\mu^2=\frac{C}{r^2}$.

@@

%{\color{gray}
%With the definition Eq.~(\ref{eq:satdef}), the saturation scale in the BGK model is given by
%\begin{equation}
%Q^2_s(x)= \frac{\pi^2 \alpha_s(\mu^2) x g(x,\mu^2)}{3 \sigma_0}.
%\end{equation}
%since $r$ correspondng to the saturation scale is 
%}
{\color{blue}
While, in principle, the dipole cross-section is impact-parameter, $b$, dependent \cite{impact}:\\
i.e.,
\begin{equation}
\sigma_{\mathrm{dp}}(x,r)=\int d^2b N(x,r,b),
\label{eq:impact}
\end{equation} 
we will consider $b$-integrated dipole cross-section.
As one can see in Eq.~(\ref{eq:impact}), $\sigma_0$ is related to the effective size of the target.% $\sigma_0=2\pi R^2$.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{$k_T$ factorization, dipole cross section, unintegrated gluon distribution and more...}
\section{The Sudakov form factor }
In this section, we discuss how the Sudakov form factor is implemented in the above saturation models. %{\color{blue} and introduce unintegrated gluon distribution.}
The dipole cross-section, $\sigma_{\mathrm{dp}}(x, r) $, and the unintegrated gluon distribution, $\mathcal{F}(x,k^2)$, are related to each other by\footnote{it can also be written $\sigma_{\mathrm{dp}}(x,r) = \frac{4 \pi}{3} \int\frac{d^2 k}{k^4} \alpha_s \mathcal{F}(x, k^2) \left(1-e^{\pm i \pairdot{k}{r}}\right) $ considering it only depends on the relative angle between $\mathbf{r}$ and $\mathbf{k}$.}
\cite{bgk2002}
\begin{align} 
\sigma_{\mathrm{dp}}(x,r) &= \frac{2 \pi}{3} \int\frac{d^2 \mathbf{k} }{k^2} \alpha_s \mathcal{F}(x, k^2) |1-e^{-i \pairdot{k}{r}}|^2,
\label{eq:ugdtosigma}\\
\alpha_s \mathcal{F}(x,k^2) &= \frac{3 }{16 \pi^3}\int d^2 \mathbf{r} e^{i \pairdot{k}{r}}  \nabla^2_{\mathbf{r}} \sigma_{\mathrm{dp}}(x,r),
\label{eq:sigmatougd}
\end{align}
%{\color{blue} $|...|^2$ can be seen in Ref.~\cite{bgk2002} Eq.~(15). Expanding \& considering rot. inv. , one can recover $1-e^{-ik\cdot r} $ with a factor 2.} 
where the unintegrated gluon distribution is related to the integrated gluon distribution, $g(x,Q^2)$, by the relation, for large $Q^2$ \cite{bgk2002},%{\color{red}(large Q only? bgk)} 
\begin{equation}
\alpha_s(Q^2) x g(x,Q^2)=\int^{Q^2}_{0} d k^2 \alpha_s \mathcal{F}(x,k^2).
\end{equation}
Following the convention of Ref.~\cite{bgk2002}, we consider an object $\alpha_s\mathcal{F}(x,k^2)\equiv\alpha_s(k^2)\mathcal{F}(x,k^2)$.

@@

%Now, by integrating over angles,
%\begin{equation}
%\sigma_{\mathrm{dp}}(x,r,Q^2) =\int^\infty_0 \frac{d k}{ k} \left( 1- J_0(k r) \right) \int^\infty_0 d {r'}  {r'}  J_0(k {r'} ) e^{-S_{pert}({r'} ,Q^2)} \nabla^2_{{r'} }\sigma_{\mathrm{dp}}(x,{r'} ).
%\end{equation}
%Finally, using 
%\begin{equation}
%\int^\infty_0 \frac{d k}{k} J_0({r'} k)(1-J_0(rk))=\log\left(\frac{r}{{r'} }\right)\theta(r-{r'} ),
%\end{equation}
%one obtains
%\begin{framed}
The above integral can be performed analytically, and one obtains
\begin{equation}
\sigma_{\mathrm{dp}}(x,r,Q^2) =\int^r _0 d {r'}   {r'}  \log\left(\frac{r}{{r'} }\right) e^{-S({r'} ,Q^2)} \nabla^2_{{r'} }\sigma_{\mathrm{dp}}(x,{r'} ).
\label{eq:gbssigma}
\end{equation}
%\end{framed}
This form of the dipole cross-section does no longer saturate to a constant value unless $S(r,Q^2)=0$, but it rises logarithmically in the large-$r$ region:
\begin{equation}
\frac{\partial \sigma(x,r,Q^2)}{\partial \log (r)}\Big|_{r\rightarrow\infty}=\int^\infty_0 dr re^{-S(r,Q^2)}\nabla_r^2\sigma(x,r)\neq0.%=\mathrm{constant} .
\end{equation}   
% ( {\color{green}this is $\lim\limits_{k^2\rightarrow0} \alpha_s\mathcal{F}(x,k^2)$}).
This, in fact, is $\alpha_s\mathcal{F}(x,0,Q^2)$, and clearly suggests modification of the small-$k$ region of the unintegrated gluon density while the improvement by the DGLAP evolution (BGK model) affected the large-$k$ region.  
As discussed above, the saturation limit, $\sigma_0$, is related to the effective size of the target, and the logarithmic rise is associated with a proton without clear boundary \cite{gbw1998}.

In the present study, we focus on the leading order of the perturbative Sudakov factor\cite{xiao2017},
\begin{equation}
S^{(1)}_{pert}=\frac{C_A }{2 \pi} \int^{Q^2}_{\mu_b^2  } \alpha(\mu^2 )\frac{d \mu^2}{\mu^2}  \log\left(\frac{Q^2}{\mu^2}\right).
\end{equation}
For the case of running coupling $\alpha_s(\mu^2)=\frac{1}{b_0 \log\left(\frac{\mu^2}{\Lambda_2}\right) }$, we get
%\begin{framed}
\begin{multline}
S^{(1)}_{pert}(r,Q) =\frac{C_A}{2 \pi b_0} \Big[-\log\left(\frac{Q^2}{\mu^2_b}\right) \\+\left(\frac{1+\alpha(\mu_b^2)  b_0 \log \left(\frac{Q^2}{\mu_b^2}\right) }{\alpha(\mu_b^2)   b_0}\right) \log\left( 1+\alpha(\mu_b^2)   b_0 \log \left(\frac{Q^2}{\mu_b^2}\right) \right) \Big],
\label{eq:sudakov}
\end{multline}
where $b_0=\frac{11 C_A-2 n_f}{12}$.
%\end{framed}
The lower limit of the integral $\mu_b=C_s/r$, where $C_s=2e^{-\gamma_E}$, and $\gamma_E \approx 0.577$ is the Euler-Mascheroni constant.\\
Two points have to be clarified in the above expression.
Firstly, the lower limit of the integration is restricted to the region $\mu_b<Q$ such that for $\mu_b>Q$, $S(r,Q)=0$. That is to say that in the limit $Q^2\rightarrow0$, the effect of the Sudakov factor nil. Consequently, for a fixed value of $Q^2$, the small-$r$ limit of the original dipole cross-section is recovered.   Such restriction is not present in the original CSS formula\cite{css1985} (See also Ref.~\cite{collins2016} for the improved treatment for small $r$.), but as we are concerned with relatively low values of $Q^2$, one needs to consider the region $1/r^2\sim k^2 >Q^2$.
In short, in the limit $Q\rightarrow 0$ we recover the original GBW/BGK model. Also in the limit $r \rightarrow 0$, again,  we recover the original GBW/BGK model.
Secondly, as the dipole size $r$ becomes large, the integration enters the non-perturbative region. In order to keep it perturbative, one can use so-called ``$b_*$-prescription'' \cite{css1985}, in which 
\begin{equation}
\mu_b^2=C_s^2/r_*^2= C_s^2/r^2+C_s^2/r_{\mathrm{max}}^2.
\end{equation}
The constant $r_{\mathrm{max}}$ is chosen such that in the large-$r$ region $\mu_b^2\simeq C_s^2/r_{\mathrm{max}}^2>>\Lambda_{\mathrm{QCD}}^2$.
In principle, one can include also the non-perturbative Sudakov factor\cite{css1985, prokudin2015}:
\begin{equation}
S(r,Q^2)= S_{pert}(r,Q^2)+S_{np}(r,Q^2),
\end{equation}
where we assume the form in Ref.~\cite{prokudin2015}
\begin{equation}
S_{np}(r,Q^2)=g_1r^2+g_2\log\left(\frac{r}{r_*}\right)\log\left(\frac{Q}{Q_0}\right).
\end{equation}
Considering that $\nabla^2_r \sigma$ in Eq.~(\ref{eq:gbssigma}) has a factor $e^{-a r^2}$, where $a$ is the appropriate factor in the respective models, it is apparent that the general behaviour of $S_{np}\sim r^2$ is already present in the models. 
The non-perturbative Sudakov factor is primarily important in the region $1/r<Q\lesssim 1/r_{\mathrm{max}}$. However, in such region, the second term is small compared to the first term, not only because of the suppression by $\log(Q/Q_0)$, but also because in the large-$r$ region, $r^2>\log\left({r}/{r_*}\right)$.  Therefore, one expects the contribution from the second term to be in the small region of not too small $Q$ and not too large $r$. One, however, needs to keep in mind that the Sudakov factor is in the integrand of the dipole cross-section Eq.~(\ref{eq:gbssigma}). That is to say that in the large-$r$ region of the dipole cross-section, it has effect from the small-$r'$ region of the integrand.
Nevertheless, the improvement by the non-perturbative Sudakov factor is less than 5\% for the BGK model and practically no improvement for the GBW model, and thus we neglect it in this study. Since diffractive DIS is more sensitive to the large-$r$ region, it may become necessary to include the non-perturbative factor in that case.

In this study, we shall employ an alternative form of $\mu_b$ proposed in Ref.~\cite{gbs2018}:
\begin{equation}
\mu_b^2= \frac{\mu_0^2}{1-e^{-r^2\frac{\mu_0^2}{C} }},
\label{eq:newstar}
\end{equation}
where $\mu_0^2=C/r_{\mathrm{max}}^2$ for both $g(x,\mu)$ and the Sudakov factor.

@@

However, for the Sudakov-improved models, studied in this work, $\sigma_0$ is no longer a constant to which dipole cross-section converges.
% Hence, we employ two new definitions.
%Hence, one tries a definition, 
%\begin{equation}
%\frac{\partial^2 \sigma}{{\partial r}^2}=0
%\end{equation}
%That is, 
%\begin{equation}
%e^{-S(r,Q)}\nabla^2_r \sigma(x,r)-\frac{1}{r^2}\int^r_0 dr' r'  e^{-S(r',Q)}\nabla^2_{r'} \sigma(x,r')=0,
%\end{equation}  
%where this condition yields for GBW model
%\begin{equation}
%2-r^2Q_s^2=0.
%\label{eq:curvature}
%%\end{equation}
%({\color{red} this means $R_0^2 =2/ Q_s^2$ that is a factor of 2 different. so equivalent of taking a point $1-e^{-1/2}\simeq 0.393 $ not 0.632})
%Now, if one, instead choses a condition
%\begin{equation}
%\frac{\partial^2 \sigma}{\partial\log( R)^2}=0,
%\end{equation}
%then
%\begin{equation}
%R^2 e^{-S(R,Q)}\nabla^2\sigma(x,R)=0.
%\end{equation}
%And thus the condition is,
%\begin{equation}
%\nabla^2\sigma(x,R)=0
%\end{equation}
%and it is independent of the Sudakov factor.\\
%This definition yields for GBW model 
%\begin{equation}
%4-r^2Q_s^2=0,
%%\end{equation}
%recovering the original relation.
There for one needs to consider an alternative definition of the saturation scale.
As an alternative form, one considers the unintegrated gluon density $\alpha_s\mathcal{F}(x,k^2)$,
and defines in terms of the transverse momentum $k$ (i.e., the Fourier conjugate variable of $r$):
\begin{equation}
 \frac{\partial \alpha_s \mathcal{F}(x,k^2)}{\partial k^2}=0.
 \label{eq:peak}
\end{equation}
Then, for the GBW model 
\begin{equation}
\frac{\partial \alpha_s \mathcal{F}(x,k^2)}{\partial k}= \frac{4 k}{Q_s^4} { e^{-\frac{k^2}{Q_s^2}}} \left(Q_s^2-k^2\right).
\end{equation}
Therefore, Eq.~\ref{eq:peak} can also be used as a definition.
The saturation defined by Eq.~(\ref{eq:peak}) corresponds to the scale at with the density of gluons is at its maximum.

@@

\begin{figure}[H]
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/F2-GBW.png}
}
%\resizebox{0.5\textwidth}{!}{
%\includegraphics{./Plots/F2-BGK.png}
%}
\caption{The structure function $F_2$ , and $x=10^{-2}, 10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
\label{F2}
\end{figure}
\begin{figure}[H]
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/slope-GBW.png}
}
\caption{The $x$-slope of $F_2$,  $\lambda_{\mathrm{eff}}=-\frac{\partial \log F_2}{\log x}$, at $Q^2=650$GeV, and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
\label{slope}
\end{figure}

>>>>

\usepackage{babel}
\usepackage[table]{xcolor}
\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{amsfonts}
\usepackage{ragged2e}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{physics}
\usepackage{hyperref}
\usepackage{ragged2e}
\usepackage{float}
\usepackage{rotating}
\usepackage{ulem}
\usepackage{authblk}

\usepackage[
backend=bibtex,
%style=ieee
maxbibnames=3,
%backend=bibtex,
style=ieee
]{biblatex}
\addbibresource{./ref/golec.bib}
\addbibresource{./ref/gbw1998.bib}
\addbibresource{./ref/bgk2002.bib}
\addbibresource{./ref/impact.bib}
\addbibresource{./ref/cambqcd.bib}
\addbibresource{./ref/gbs2018.bib}
\addbibresource{./ref/gbs2006.bib}
\addbibresource{./ref/xiao2017.bib}
\addbibresource{./ref/minuit.bib}
\addbibresource{./ref/hera.bib}
\addbibresource{./ref/jk2006.bib}
\addbibresource{./ref/FL.bib}
\addbibresource{./ref/stasto2018.bib}
\addbibresource{./ref/stebel2020.bib}
\addbibresource{./ref/ellis1996.bib}
\addbibresource{./ref/bronstein.bib}
\addbibresource{./ref/mueller2016.bib}
\addbibresource{./ref/css1985.bib}
\addbibresource{./ref/prokudin2015.bib}
\addbibresource{./ref/collins2016.bib}

\newcommand{\pairdot}[2]{ \mathbf{#1}\cdot\mathbf{#2}  }
\begin{document}
\author{Krzystof Kutak, Sebastian Sapeta, Tomoki Goda
}	 
\title{ Effects of Sudakov form factor in\\ the
Golec-Biernat W\"usthoff saturation model}
\date{\today}
%\frontmatter
\maketitle
%\tableofcontents

@@

\section{GBW and BGK models }
In Ref.~\cite{gbw1998}, the following form of the dipole cross-section was proposed:
\begin{equation}
\sigma_{\mathrm{GBW}}(x ,r )=\sigma_{0} \left(1-e^{-\frac{r^2}{4} Q_0^2\left(\frac{x_0}{x}\right)^{\lambda} }\right),
\label{eq:gbw}
\end{equation}
and a modified variable 
\begin{equation}
x_m=x \left(1+\frac{4 m_f^2}{Q^2}\right),
\label{eq:modx}
\end{equation}
where $m_f$ is an effective mass of a quark $f$,
was used in place of the Bjorken scaling variable $x$. In the rest of this paper, the subscript $m$ is dropped. Along with the above modification, effective mass of the light quarks $m_l=0.14\mathrm{GeV}$ was introduced in order to study the photoproduction limit ($Q^2\rightarrow0$) of DIS.

The GBW model incorporates two main features which characterize two regions of $r$ separated by the saturation scale $Q_s(x)$, which we discuss in detail later.
The first behaviour, 
\begin{align}
&& \sigma(x,r)&\sim r^2 & r&\ll 2/Q_s(x),
\end{align}
is related to the QCD (colour transparency), that is to say that the smaller the dipole, the less visible (colourless) it is to the target. 
The second behaviour,
\begin{align}
&& \sigma(x,r)&\sim \sigma_0 & r&\gg 2/Q_s(x),
\end{align}
is related to the saturation phenomenon. \\

The GBW model in the small-$r$ limit behaves as 
\begin{equation}
\sigma_{\mathrm{GBW}}\simeq\frac{r^2}{4} Q_0^2\left(\frac{x_0}{x}\right)^{\lambda}.
\end{equation}
However, the small-$r$ limit of the dipole cross-section is \cite{bgk2002}, 
\begin{equation}
\sigma_{\mathrm{dp}}(x,r)\simeq \frac{\pi^2 r^2\alpha_s(\mu^2) x g(x,\mu^2)}{3},
\end{equation}
where $g(x,\mu^2)$ is the integrated gluon distribution at the scale $\mu^2=\frac{C}{r^2}$.

@@

While, in principle, the dipole cross-section is impact-parameter, $b$, dependent \cite{impact}:\\
i.e.,
\begin{equation}
\sigma_{\mathrm{dp}}(x,r)=\int d^2b N(x,r,b),
\label{eq:impact}
\end{equation} 
we will consider $b$-integrated dipole cross-section.
As one can see in Eq.~(\ref{eq:impact}), $\sigma_0$ is related to the effective size of the target.% $\sigma_0=2\pi R^2$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{$k_T$ factorization, dipole cross section, unintegrated gluon distribution and more...}
\section{The Sudakov form factor }
In this section, we discuss how the Sudakov form factor is implemented in the above saturation models. %{\color{blue} and introduce unintegrated gluon distribution.}
The dipole cross-section, $\sigma_{\mathrm{dp}}(x, r) $, and the unintegrated gluon distribution, $\mathcal{F}(x,k^2)$, are related to each other by\footnote{it can also be written $\sigma_{\mathrm{dp}}(x,r) = \frac{4 \pi}{3} \int\frac{d^2 k}{k^4} \alpha_s \mathcal{F}(x, k^2) \left(1-e^{\pm i \pairdot{k}{r}}\right) $, considering it only depends on the relative angle between $\mathbf{r}$ and $\mathbf{k}$.}
\cite{bgk2002}
\begin{align} 
\sigma_{\mathrm{dp}}(x,r) &= \frac{2 \pi}{3} \int\frac{d^2 \mathbf{k} }{k^2} \alpha_s \mathcal{F}(x, k^2) |1-e^{-i \pairdot{k}{r}}|^2,
\label{eq:ugdtosigma}\\
\alpha_s \mathcal{F}(x,k^2) &= \frac{3 }{16 \pi^3}\int d^2 \mathbf{r} e^{i \pairdot{k}{r}}  \nabla^2_{\mathbf{r}} \sigma_{\mathrm{dp}}(x,r),
\label{eq:sigmatougd}
\end{align}
%{\color{blue} $|...|^2$ can be seen in Ref.~\cite{bgk2002} Eq.~(15). Expanding \& considering rot. inv. , one can recover $1-e^{-ik\cdot r} $ with a factor 2.} 
where the unintegrated gluon distribution is related to the integrated gluon distribution, $g(x,Q^2)$, by the relation, for large $Q^2$ \cite{bgk2002},%{\color{red}(large Q only? bgk)} 
\begin{equation}
\alpha_s(Q^2) x g(x,Q^2)=\int^{Q^2}_{0} d k^2 \alpha_s \mathcal{F}(x,k^2).
\end{equation}
Following the convention of Ref.~\cite{bgk2002}, we consider an object $\alpha_s\mathcal{F}(x,k^2)\equiv\alpha_s(k^2)\mathcal{F}(x,k^2)$.

@@

The above integral can be performed analytically, and one obtains
\begin{equation}
\sigma_{\mathrm{dp}}(x,r,Q^2) =\int^r _0 d {r'}   {r'}  \log\left(\frac{r}{{r'} }\right) e^{-S({r'} ,Q^2)} \nabla^2_{{r'} }\sigma_{\mathrm{dp}}(x,{r'} ).
\label{eq:gbssigma}
\end{equation}
%\end{framed}
This form of the dipole cross-section does no longer saturate to a constant value unless $S(r,Q^2)=0$, but it rises logarithmically in the large-$r$ region:
\begin{equation}
\frac{\partial \sigma(x,r,Q^2)}{\partial \log (r)}\Big|_{r\rightarrow\infty}=\int^\infty_0 dr re^{-S(r,Q^2)}\nabla_r^2\sigma(x,r)\neq0.%=\mathrm{constant} .
\end{equation}   
% ( {\color{green}this is $\lim\limits_{k^2\rightarrow0} \alpha_s\mathcal{F}(x,k^2)$}).
This, in fact, is $\alpha_s\mathcal{F}(x,0,Q^2)$, and clearly suggests modification of the small-$k$ region of the unintegrated gluon density while the improvement by the DGLAP evolution (BGK model) affected the large-$k$ region.  
As discussed above, the saturation limit, $\sigma_0$, is related to the effective size of the target, and the logarithmic rise is associated with a proton without clear boundary \cite{gbw1998}.

In the present study, we focus on the leading order of the perturbative Sudakov factor\cite{xiao2017},
\begin{equation}
S^{(1)}_\mathrm{pert}=\frac{C_A }{2 \pi} \int^{Q^2}_{\mu_b^2  } \alpha(\mu^2 )\frac{d \mu^2}{\mu^2}  \log\left(\frac{Q^2}{\mu^2}\right).
\end{equation}
For the case of running coupling $\alpha_s(\mu^2)=\frac{1}{b_0 \log\left(\frac{\mu^2}{\Lambda_2}\right) }$, we get
%\begin{framed}
\begin{multline}
S^{(1)}_\mathrm{pert}(r,Q) =\frac{C_A}{2 \pi b_0} \Big[-\log\left(\frac{Q^2}{\mu^2_b}\right) \\+\left(\frac{1+\alpha(\mu_b^2)  b_0 \log \left(\frac{Q^2}{\mu_b^2}\right) }{\alpha(\mu_b^2)   b_0}\right) \log\left( 1+\alpha(\mu_b^2)   b_0 \log \left(\frac{Q^2}{\mu_b^2}\right) \right) \Big],
\label{eq:sudakov}
\end{multline}
where $b_0=\frac{11 C_A-2 n_f}{12}$.
%\end{framed}
The lower limit of the integral $\mu_b=C_\mathrm{S}/r$, where $C_\mathrm{S}=2e^{-\gamma_\mathrm{E}}$, and $\gamma_\mathrm{E} \approx 0.577$ is the Euler-Mascheroni constant.\\
Two points have to be clarified in the above expression.
Firstly, the lower limit of the integration is restricted to the region $\mu_b<Q$ such that for $\mu_b>Q$, $S(r,Q)=0$. That is to say that in the limit $Q^2\rightarrow0$, the effect of the Sudakov factor nil. Consequently, for a fixed value of $Q^2$, the small-$r$ limit of the original dipole cross-section is recovered.   Such restriction is not present in the original CSS formula\cite{css1985} (See also Ref.~\cite{collins2016} for the improved treatment for small $r$.), but as we are concerned with relatively low values of $Q^2$, one needs to consider the region $1/r^2\sim k^2 >Q^2$.
In short, in the limit $Q\rightarrow 0$ we recover the original GBW/BGK model. Also in the limit $r \rightarrow 0$, again,  we recover the original GBW/BGK model.
Secondly, as the dipole size $r$ becomes large, the integration enters the non-perturbative region. In order to keep it perturbative, one can use so-called ``$b_*$-prescription'' \cite{css1985}, in which 
\begin{equation}
\mu_b^2=C_\mathrm{S}^2/r_*^2= C_\mathrm{S}^2/r^2+C_\mathrm{S}^2/r_{\mathrm{max}}^2.
\end{equation}
The constant $r_{\mathrm{max}}$ is chosen such that in the large-$r$ region $\mu_b^2\simeq C_\mathrm{S}^2/r_{\mathrm{max}}^2>>\Lambda_{\mathrm{QCD}}^2$.
In principle, one can include also the non-perturbative Sudakov factor\cite{css1985, prokudin2015}:
\begin{equation}
S(r,Q^2)= S_\mathrm{pert}(r,Q^2)+S_\mathrm{np}(r,Q^2),
\end{equation}
where we assume the form in Ref.~\cite{prokudin2015}
\begin{equation}
S_\mathrm{np}(r,Q^2)=g_1r^2+g_2\log\left(\frac{r}{r_*}\right)\log\left(\frac{Q}{Q_0}\right).
\end{equation}
Considering that $\nabla^2_r \sigma$ in Eq.~(\ref{eq:gbssigma}) has a factor $e^{-a r^2}$, where $a$ is the appropriate factor in the respective models, it is apparent that the general behaviour of $S_\mathrm{np}\sim r^2$ is already present in the models. 
The non-perturbative Sudakov factor is primarily important in the region $1/r<Q\lesssim 1/r_{\mathrm{max}}$. However, in such region, the second term is small compared to the first term, not only because of the suppression by $\log(Q/Q_0)$, but also because in the large-$r$ region, $r^2>\log\left({r}/{r_*}\right)$.  Therefore, one expects the contribution of the second term to be comparatively smaller than that of the $\sim r^2$ term, and only possible region where it may contribute is confined in the small region of not too small $Q$ and not too large $r$. One, however, needs to keep in mind that the Sudakov factor is in the integrand of the dipole cross-section Eq.~(\ref{eq:gbssigma}). That is to say that in the large-$r$ region of the dipole cross-section, it has effect from the small-$r'$ region of the integrand.
Nevertheless, as we briefly discuss later in section~5, the improvement by the non-perturbative Sudakov factor is less than 5\% for the BGK model and practically no improvement for the GBW model, and thus we neglect it in this study. Since diffractive DIS is more sensitive to the large-$r$ region, it may become necessary to include the non-perturbative factor in that case.

In this study, we shall employ for both $g(x,\mu)$ and the Sudakov factor an alternative form of $\mu_b$ proposed in Ref.~\cite{gbs2018}:
\begin{equation}
\mu_b^2= \frac{\mu_0^2}{1-e^{-r^2\frac{\mu_0^2}{C} }},
\label{eq:newstar}
\end{equation}
where $\mu_0^2=C/r_{\mathrm{max}}^2$.

@@

However, for the Sudakov-improved models, studied in this work, $\sigma_0$ is no longer a constant to which dipole cross-section converges.
% Hence, we employ two new definitions.
%Hence, one tries a definition, 
%\begin{equation}
%\frac{\partial^2 \sigma}{{\partial r}^2}=0
%\end{equation}
%That is, 
%\begin{equation}
%e^{-S(r,Q)}\nabla^2_r \sigma(x,r)-\frac{1}{r^2}\int^r_0 dr' r'  e^{-S(r',Q)}\nabla^2_{r'} \sigma(x,r')=0,
%\end{equation}  
%where this condition yields for GBW model
%\begin{equation}
%2-r^2Q_s^2=0.
%\label{eq:curvature}
%%\end{equation}
%({\color{red} this means $R_0^2 =2/ Q_s^2$ that is a factor of 2 different. so equivalent of taking a point $1-e^{-1/2}\simeq 0.393 $ not 0.632})
%Now, if one, instead choses a condition
%\begin{equation}
%\frac{\partial^2 \sigma}{\partial\log( R)^2}=0,
%\end{equation}
%then
%\begin{equation}
%R^2 e^{-S(R,Q)}\nabla^2\sigma(x,R)=0.
%\end{equation}
%And thus the condition is,
%\begin{equation}
%\nabla^2\sigma(x,R)=0
%\end{equation}
%and it is independent of the Sudakov factor.\\
%This definition yields for GBW model 
%\begin{equation}
%4-r^2Q_s^2=0,
%%\end{equation}
%recovering the original relation.
Therefore, one needs to consider an alternative definition of the saturation scale.
As an alternative form, one considers the unintegrated gluon density $\alpha_s\mathcal{F}(x,k^2)$,
and defines in terms of the transverse momentum $k$ (i.e., the Fourier conjugate variable of $r$):
\begin{equation}
 \frac{\partial \alpha_s \mathcal{F}(x,k^2)}{\partial k^2}=0.
 \label{eq:peak}
\end{equation}
Then, for the GBW model 
\begin{equation}
\frac{\partial \alpha_s \mathcal{F}(x,k^2)}{\partial k}= \frac{4 k}{Q_s^4} { e^{-\frac{k^2}{Q_s^2}}} \left(Q_s^2-k^2\right).
\end{equation}
Therefore, Eq.~\ref{eq:peak} can also be used as a definition.
The saturation defined by Eq.~(\ref{eq:peak}) corresponds to the scale at which the density of gluons is at its maximum.

@@

\begin{figure}[H]
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/F2-GBW.png}
}
%\resizebox{0.5\textwidth}{!}{
%\includegraphics{./Plots/F2-BGK.png}
%}
\caption{The structure function $F_2$ , and $x=10^{-2}, 10^{-4}, 10^{-6}$ (from bottom to top).\\Left: GBW, Right: BGK}
\label{F2}
\end{figure}
\begin{figure}[H]
\resizebox{\textwidth}{!}{
\includegraphics{./Plots/slope-GBW.png}
}
\caption{The $x$-slope of $F_2$,  $\lambda_\mathrm{eff}=-\frac{\partial \log F_2}{\log x}$,  and $x=10^{-2},10^{-4}, 10^{-6}$ (from bottom to top). The slope is generally lowered, and this can be seen also in Figs.~\ref{fig:gridGBW} and \ref{fig:gridBGK}\\Left: GBW, Right: BGK}
\label{slope}
\end{figure}
